Approximate Sequencing of Virtual Reels with Genetic Algorithms

### 2020-06-20 Approximate-Sequencing-of-Virtual-Reels-with-Genetic-Algorithms/paper.tex
Experimental data was added.

The fitness value estimation is done from the list of chunks, but crossover and mutation are done over candidate sequences. Such a change in the candidate sequences leads to an immediate recalculation of chunks samples. Modified uniform crossover is used with the application of normal distribution (mean 50\% and a standard deviation of 20\%) for the rate of participation of the two parents. It means that one of the parents has more influence in forming the offspring. Because the length of the original sequence is generally unknown the size of the offspring sequence length should be estimated during crossover process. As a lower bound of candidate sequence length, the number of unique symbols in the virtual reels is taken. As an upper bound of candidate sequence length, the total length of all chunks taken together is taken. Such estimation of the candidate sequence length gives chance all symbols to participate (lower bound) and all chunks to be used in a single sequence (upper bound). Such an estimation of the length gives chance to the genetic algorithm to optimize this parameter too. The mutation is done by random replacement of a single value in the candidate sequence. The random value is taken from the chunks of the original sequence.

>>>>

The fitness value estimation is done from the list of chunks, but crossover and mutation are done over candidate sequences. Such a change in the candidate sequences leads to an immediate recalculation of chunks samples. Modified uniform crossover is used with the application of normal distribution (mean 50\% and a standard deviation of 20\%) for the rate of participation of the two parents. It means that one of the parents has more influence in forming the offspring. Because the length of the original sequence is generally unknown the size of the offspring sequence length should be estimated during crossover process. As a lower bound of candidate sequence length, the number of unique symbols in the virtual reels is taken. As an upper bound of candidate sequence length, the total length of all chunks taken together is taken. Such estimation of the candidate sequence length gives chance all symbols to participate (lower bound) and all chunks to be used in a single sequence (upper bound). Such an estimation of the length gives chance to the genetic algorithm to optimize this parameter too. Almost in all cases, parents are at different lengths. The offspring differs in length from parents too. When the offspring is longer than the parents, values are taken in a loop from the beginning. It is the natural way to produce longer offspring because virtual reels are used in looping during real-time game operation. The mutation is done by random replacement of a single value in the candidate sequence. The random value is taken from the chunks of the original sequence.
